---
title: "Libraries in Lockbox"
author: "Robert Krzyzanowski"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Libraries in Lockbox (Technical Notes)}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

# Usage of libraries in lockbox

Understanding the technical design of lockbox requires some knowledge of how R tracks and
installs packages. As explained by Hadley in his [R package development book](http://r-pkgs.had.co.nz/package.html#library), R packages are stored in **libraries**; a library is simply a directory containing the
code for one or more R packages. R looks for packages by traversing over each library and 
detecting whether it contains the package in question. You can see what libraries you
are using (usually one default) with

```{r}
.libPaths()
```

However, the limitation is that you can only have one version installed of each package. The structure
of an R library looks like:

  * first_package
    * DESCRIPTION
    * Other files...
  * second_package
    * DESCRIPTION
    * Other files...
  * ...
  
To overcome this limitation and provide the ability to load different versions of the same package,
lockbox creates an entirely new directory (by default in `~/.R/lockbox`, but customizable using
the `lockbox.directory` option) with the following structure:

  * first_package
    * 0.1.0
      * DESCRIPTION
      * ...
    * 0.1.1
      * DESCRIPTION
      * ...
  * second_package
    * 1.0.1
      * DESCRIPTION
      * ...
    * 1.0.2
      * DESCRIPTION
      * ...
  * ...
  
In other words, the lockbox directory contains code for *different versions* of each package. However, this 
means it cannot be used directly as an R library, because the R runtime expects a flat structure with the
package's contents in each subdirectory.


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(avant::variable_definitions()[1:2, ])
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
